Forecasting Gamma-ray Bursts using Gravitational Waves

### 2018-03-20 Paper/Manuscript.tex
abstract fix

\begin{abstract}
We explore the intriguing possibility of employing future ground-based gravitational-wave interferometers to detect the inspiral of binary neutron stars early enough to alert the electromagnetic observatories so that a gamma-ray burst (GRB) can be observed in its entirety from its very start.
We quantify the ability to predict a GRB by computing the time a binary neutron star (BNS) system takes to inspiral from a its moment of detection to its final merger. We define the moment of detection to be given when the inteferometer network accumulates a signal-to-noise ratio of 15. %for the BNS inspiral.
For our computations, %of advance warning times, 
we specifically consider BNS systems at luminosity distances of (i) $D\le200\,$Mpc in the three-interferometer Advanced-LIGO-Virgo network of 2020, and (ii) $D \le 1000\,$Mpc in the Einstein Telescope's B and C configurations. 
In the case of Advanced LIGO-Virgo we find that we may at best get a few minutes of warning time thus we expect no forecast of GRBs in the 2020s. 
On the other hand, we demonstrate that Einstein Telescope will provide us with warning times as long as a few hours, more specifically, greater than an hour
for BNS inspirals closer than roughly 600\,Mpc. Taking this luminosity distance to be our horizon distance, 
we show that we expect to forecast $\gtrsim \ord(10^2)$ GRBs in the 2030s using the C configuration of Einstein Telescope.
We reapply our computation to binary black hole - neutron star inspirals and find that we expect 1 to 3 tidal disruption events 
to be forecast by the same detector.
%Our main conclusions are: (i) we expect ALV network to forecast 1 to 3 GRBs in the 2020s, (ii)

>>>>

\begin{abstract}
We explore the intriguing possibility of employing future ground-based gravitational-wave interferometers to detect the inspiral of binary neutron stars early enough to alert the electromagnetic observatories so that a gamma-ray burst (GRB) can be observed in its entirety from its very start.
We quantify the ability to predict a GRB by computing the time a binary neutron star (BNS) system takes to inspiral from its moment of detection to its final merger. We define the moment of detection to be the instant at which the inteferometer network accumulates a signal-to-noise ratio of 15. %for the BNS inspiral.
For our computations, %of advance warning times, 
we specifically consider BNS systems at luminosity distances of (i) $D\le200\,$Mpc in the three-interferometer Advanced-LIGO-Virgo network of 2020, and (ii) $D \le 1000\,$Mpc in the Einstein Telescope's B and C configurations. 
In the case of Advanced LIGO-Virgo we find that we may at best get a few minutes of warning time thus we expect no forecast of GRBs in the 2020s. 
On the other hand, we demonstrate that Einstein Telescope will provide us with warning times as long as a few hours.  
Taking one hour as a benchmark warning time, we obtain a corresponding horizon
distance of roughly 600 Mpc for Einstein C.
%, more specifically, greater than an hour
%for BNS inspirals closer than roughly 600\,Mpc. Taking this luminosity distance to be our horizon distance, 
Using current BNS event rates within this horizon distance, we show that we expect to forecast $\gtrsim \ord(10^2)$ GRBs in the 2030s with the C configuration of Einstein Telescope.
We reapply our warning-time computation to binary black hole - neutron star inspirals and find that we expect 1 to 3 tidal disruption events 
to be forecast by the same detector.
%Our main conclusions are: (i) we expect ALV network to forecast 1 to 3 GRBs in the 2020s, (ii)
